### 2023-10-24 state/gru.tex
Bunch of changes, added design gru
Gru changes

\section{\acs{GRU}}
The \acf{GRU} is another type of \ac{RNN}. It is also known to reduce the effect of the vanishing gradient problem. It was first introduced to improve translation techniques \cite{gru}.

@@

While the \ac{GRU} is its own type of \ac{RNN}, it has been compared and assimilated to an \ac{LSTM} \cite{nbLSTM}. Indeed, the subtype of \ac{LSTM} it has been associated with is called the \ac{CIFG} \ac{LSTM}. If the input and forget gates are combined into one ($f_t=\overrightarrow{1}-i_t$), they can be assimilated as the update gate of the \ac{GRU}. The reset gate would then be the \ac{LSTM}'s output gate.

>>>>

\section{\acs{GRU}}\label{sec:gru}
The \acf{GRU} is another type of \ac{RNN}. It is also known to reduce the effect of the vanishing gradient problem. It was first introduced to improve translation techniques \cite{gru}.

@@

While the \ac{GRU} is its own type of \ac{RNN}, it has been compared and assimilated to an \ac{LSTM} \cite{nbLSTM}. Indeed, the subtype of \ac{LSTM} it has been associated with is called the \ac{CIFG} \ac{LSTM}. If the input and forget gates are combined into one ($\overrightarrow{f_t}=\overrightarrow{1}-\overrightarrow{i_t}$), they can be assimilated as the update gate of the \ac{GRU}. The reset gate would then be the \ac{LSTM}'s output gate.
